---
title: "Title"
author: "Huy Nguyen"
date: ""
output:
  md_document:
    variant: markdown_github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("G:/Other computers/My MacBook Air/Source/R/garchvar-in-forex-rm")
#setwd("/Users/hng/Personal Vault/Source/R/garchvar-in-forex-rm")
```

## INTRODUCTION
<div align="justify">The aim of this study is to figure out how much risk is associated with changes in the value of the GBP/VND currency pair over a period of 5 years using the GARCH VaR approach by Ionas Kelepouris & Dimos Kelepouris. The time series used in this research consists of GBP/VND returns over the past 5 years. To break it down, I use the GARCH model to estimate how much the volatility of these returns varies over time then make a forecast about potential future losses (VaR) associated with the GBP/VND currency pair. The final output will be used to create a scenario for hedging in the FX market.

## DATA EXPLORATORY
<div align="justify">This research used a dataset of 1250 observations, reflecting the fluctuations in the GBP to VND exchange rate over a span of 5 years, on a daily basis.The first 1000 obs will be used in the model and 250 obs will be used in backtesting progress.

```{r code 1, message= FALSE, warning = FALSE}
library(zoo)
library(ggplot2)
library(tseries)
library(FinTS)
library(rugarch)
df <- read.csv("GBP_VND.csv")
df$date <- as.Date(df$date, format = "%d/%m/%Y")
train_percentage <- 0.8
train_rows <- round(nrow(df) * train_percentage)
train_data <- df[1:train_rows, ]
test_data <- df[(train_rows + 1):nrow(df), ]
```

```{r code 2, message= FALSE, warning = FALSE}
head(train_data,5)
```

```{r code 3, message= FALSE, warning = FALSE}
ggplot(train_data, aes(x = date, y = price)) +
  geom_line(color = 'red') +
  labs(x = '', y = 'Price (per GBP)', title = 'GBP/VND')
adf.test(train_data$price)
```

<div align="justify">The ADF test result with a p-value of 0.3028, which is higher than the significance level of 0.05, we cannot reject the null hypothesis. This suggests that the exchange rate between GBP and VND is likely not stationary. This conclusion aligns with the graphical analysis of the price graph.Non-stationary processes have means, variances and covariances that change over time. Using non-stationary time series data leads to unreliable forecasting. For the stationarity transformation, we prefer to calculate the simple daily returns:  
$$ r_t = \frac{{\text{{price}}_t - \text{{price}}_{t-1}}}{{\text{{price}}_{t-1}}} $$

```{r code , message= FALSE, warning = FALSE}
ggplot(train_data, aes(x = date, y = return)) +
  geom_line(color = 'blue') +
  labs(x = '', y = 'Return', title = 'GBP/VND')
adf.test(na.omit(train_data$return))
```

<div align="justify">The ADF test result with a p-value of 0.01, we can reject the null hypothesis: The return series does not have a unit root and is stationary. Hence, it could be used in time series forecasting.

## GARCH Implementation
### Applying ARIMA to find the best fit of a Time Series model

# ```{r code 4, message= FALSE, warning = FALSE}
# jarque.bera.test(na.omit(df$return))
# ```


```{r code 9, message= FALSE, warning = FALSE}
ArchTest(train_data$return, lags = 1, demean = T)
```

```{r code 10, message= FALSE, warning = FALSE}
data_fit_sqrt <- train_data$return^2
plot(data_fit_sqrt, type = "l")
pacf(na.omit(data_fit_sqrt))
```

# ```{r code 11, message= FALSE, warning = FALSE}
# model_spec = ugarchspec(variance.model = 
#                           list(model = 'sGARCH', 
#                                garchOrder = c(1 , 1)), 
#                           mean.model = list(armaOrder = c(0 , 0)))
# model_fit = ugarchfit(spec = model_spec , 
#                       data = data_fit , 
#                       solver = 'solnp',
#                       out.sample=250)
# options(scipen = 999)
# model_fit@fit$matcoef
# ```
# 
# ```{r code 12, message= FALSE, warning = FALSE}
# model_roll = ugarchroll(spec = model_spec, 
#                         data = data_fit, 
#                         n.start = 999, 
#                         refit.every = 1,
#                         refit.window = 'moving')
# ```
# 
# ```{r code 13, message= FALSE, warning = FALSE}
# ArchTest(data_fit, lags = 1, demean = T)
# ```

# ```{r code 7, message= FALSE, warning = FALSE}
# fitdist(distribution = 'std' , x = data_fit)$pars
# ```
